\documentclass{article}

\usepackage[a4paper,left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tikz}

\begin{document}

\setlength\parindent{0pt}
\setlength{\parskip}{.8em} 
\pagenumbering{gobble}
\titlespacing\section{0pt}{0pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\setlist[itemize]{leftmargin=*}

% https://tex.stackexchange.com/questions/488961/correct-way-of-drawing-empty-half-filled-and-fully-filled-circles/488963
\newcommand*\emptycirc[1][1ex]{\tikz\draw (0,0) circle (#1);}
\newcommand*\fullcirc[1][1ex]{\tikz\fill (0,0) circle (#1);}

% https://tex.stackexchange.com/questions/300207/repeat-characters-n-times
\newcount\myloopcounter
\newcommand{\repeatit}[2][10]{%
  \myloopcounter0% initialize the loop counter
  \loop\ifnum\myloopcounter < #1 % Test if the loop counter is < #1
  #2%
  \advance\myloopcounter by 1 % 
  \repeat % start again
}

\begin{center}
\begin{huge}
\textbf{MAX STANLEY}
\end{huge}

Gloucestershire, UK
|
jobs@maxstanley.uk
|
github.com/maxstanley
|
https://maxstanley.uk

\end{center}

\section*{About Me}

I am a highly driven individual with 3 years experience working in multiple teams whilst working on a Degree Apprenticeship.
I took these opportunities to learn about the teams' technology stack, getting up to speed quickly on their product and making meaningful contributions.

Over this time I have become proficient in a variety of programming languages from C/C++ to Typescript and Python.
The Apprenticeship has provided me with an excellent opportunity to learn a range of soft and technical skills which I will be taking forward as I continue to develop new skills.

\section*{Experience}

\textbf{Junior Software Engineer} - UK Civil Service \hfill 09/2020 - Present

\begin{multicols}{2}
\begin{itemize}
\itemsep0em
	\item Performance Award recognising the work performed whilst an Apprentice being consistently above the level of my role.
	\item Using C/C++ to create resource efficient applications.
	\item Using GoLang to create CLI to communicate with RESTful API.
	\item Utilising the MERN stack to enable customers use of our products, and introducing modern development practices such as linting, unit-testing and Docker.
	\item Identified a need for an integration testing environment for teams tools and co-created using GoLang and Gherkin BDD.
	\item Co-lead on integration testing tool project, requiring managing customer requirements, ensuring tickets are correctly prioritised and assigning work to colleagues.
	\item Introduced colleagues to Infrastructure-as-Code tooling to enable them to share repeatable environments to support their current projects.
	\item Authored a report understanding the human impact of Agile development.
	\item Supported the onboarding of colleagues on short-term placements, upskilling them on our technology stack and assigning them appropriate tasks that support their development whilst also contributing the teams goals.
	\item Used Git Version Control to work collaboratively with colleagues on projects.
	\item Receptive to colleagues feedback on Peer Reviews, whilst also providing relevant comments on their reviews.
	\item Pair-Programmed with colleagues to use our combined knowledge of the project and surrounding tooling to create solutions more effectively than we could have separately.
\end{itemize}
\end{multicols}

\textbf{Placement Projects} - UK Civil Service \hfill 09/2019 - 04/2020

\begin{multicols}{2}
\begin{itemize}
\itemsep0em
	\item Prototyping a change to an Open Source project to demonstrate how the project could be used to enable the teams objectives.
	\item Adding a feature to an Angular site that performs full text search utilising Elastic Search.
	\item Balancing assigned work with the current team goals. Ensuring I managed by time to complete projects on schedule whilst being flexible to pick up quick turn around work to support the team.
	\item Research Project on Insider Threat Maturity Models.
	\item Using Python Pandas to analyse big data and creating visualisations to understand trends.
	\item Wrote a Mongo-Express application during first 8 week placement.
\end{itemize}
\end{multicols}

\textbf{Personal GitHub Projects} \hfill 06/2020 - Present

\begin{multicols}{2}
\begin{itemize}
\itemsep0em
	\item Used to supplement learning with practical application of knowledge.
	\item Working in a pair to create applications that can work with Kafka with different languages and testing Concourse-CI. (Request Access)
	\item \textbf{rust-prompt} - Reimplementation of go-prompt in Rust.
	\item \textbf{tango} - Trialling GoLang API Frameworks and allowing same functions to be used across frameworks.
	\item \textbf{ordering} - Created a live ordering Web Application using MERN stack for use in small restaurants. This project was used to learn about WebSocket Connections.
	\item \textbf{maxstanley.uk} - Created a blogging platform to provide myself an area to write posts that support my own and others learning. This was written without the use of JavaScript to challenge myself and to improve the accessibility of the site for those with limited internet connectivity.
\end{itemize}
\end{multicols}

\clearpage

\section*{Skills and Interests}

\begin{center}
\begin{tabular}{ c | c | c | c } 
	\textbf{Programming Languages}                                                 & \textbf{Technologies} & \textbf{Skills}  & \textbf{Interests}           \\

	                                                                               &                       &                  &                              \\
	C++17 \hfill \repeatit[4]{ \fullcirc[1ex]} \repeatit[1]{\emptycirc[1ex] }      & React                 & Highly Adaptable & Rust                         \\
	GoLang \hfill \repeatit[4]{ \fullcirc[1ex]} \repeatit[1]{\emptycirc[1ex] }     & Docker                & Avid Learner     & Microservice Architectures   \\
	TypeScript \hfill \repeatit[3]{ \fullcirc[1ex]} \repeatit[2]{\emptycirc[1ex] } & NodeJS                & Agile            & Site Reliability Engineering \\
	Python \hfill \repeatit[3]{ \fullcirc[1ex]} \repeatit[2]{\emptycirc[1ex] }     & Git                   & Collaborative    & DevSecOps                    \\
	Java \hfill \repeatit[2]{ \fullcirc[1ex]} \repeatit[3]{\emptycirc[1ex] }       & SQL                   &                  & Continuous Delivery          \\
	                                                                               & Vim                   &                  &                              \\
	                                                                               & Mongo                 &                  &                              \\
	                                                                               & AWS                   &                  &                              \\
	                                                                               & Linux                 &                  &                              \\

\end{tabular}
\end{center}

\section*{Education}

\textbf{Integrated BSc (Hons) Cyber Security Apprenticeship} - UK Civil Service \hfill 09/2018 - 09/2021

\begin{multicols}{2}
\begin{itemize}
\itemsep0em
	\item Attained a provisional First overall.
	\item Managing time between university modules and work placements.
	\item Working collaboratively with colleagues on group projects.
	\item Explaining concepts to colleagues ensuring everyone has an understanding of the module content.
\end{itemize}
\end{multicols}

\begin{center}
	\textbf{Year 3} | Cloud | Data Analytics \& ML | Incident Response \& Malware Analysis | Secure Software

	\textbf{Year 2} | Java | Network Services | Penetration Testing | Information Assurance

	\textbf{Year 1} | Computer Systems | Networks | C | Cyber Security | Python | JavaScript | Databases
\end{center}

\textbf{Extended Project Qualification} - Solihull School \hfill 09/2016 - 06/2017

\begin{multicols}{2}
\begin{itemize}
\itemsep0em
	\item Self-Motivated Project.
	\item Gathering requirements and scoping features with School IT Director.
	\item Created a Room Booking System using DotNet Core to replace the Microsoft Access solution.
	\item Introduction to independent learning of technical principles.
	\item Managing the customer relationship and adjusting features based on time constraints.
\end{itemize}
\end{multicols}

\textbf{A Levels} - Solihull School \hfill 09/2016 - 06/2018

\begin{center}
Maths | Physics | Religious Studies \& Philosophy
\end{center}

\textbf{GCSEs} - Solihull School \hfill 09/2014 - 06/2016
\begin{center}
Maths | Physics | Chemistry | Biology | English Literature \& Language

Religious Studies \& Philosophy | German | IT | Geography
\end{center}

\section*{Hobbies}

\begin{center}
Hiking | Formula 1 | Rugby | Tennis | Hack The Box
\end{center}

After learning valuable leadership and team working skills whilst in my schools CCF, once I left the school I continued to support the effort for future school cohorts to have the same experience and opportunities that I had, by volunteering to join on the expeditions.

\section*{Referees}

Referees are available upon request.

\end{document}
